MLH1 Results Outline

### 2020-02-12 doc/Results.rmd
mostly finished with pp

#### Q1. SC_HetC_M2

@@

@@

<!--  main DFs for this section

Male.poly.Mouse.Table_BivData_4MM

Bivalent_1o2  (for logistic regression, 1CO and 2COs)
male.long.biv

remember the 3 predictions for subsp;

i) Dom, no difference

ii) Musc, PWD and SKIVE greater than others

iii) Mol, MSM > MOLF

@@

>>>>

@@

```{r Q1.SC.show.long.biv, echo=FALSE}

mouse.shoo.long.biv <- ggplot(real.long.bivData, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Mouse av. \nMale Long Biv SC Lengths")
mouse.shoo.long.biv

```{r Q2.SC.long.biv, echo=FALSE}
male.long.biv <- real.long.bivData %>% filter(sex== "male")

Q1.long.biv_cell_table <- ddply(real.long.bivData, c("fileName"), summarise,

                        n_obs = length(Obj.ID),
                         mean.sc = mean(chromosomeLength)
                         )
Q1.long.biv_cell_table <- add_mouse(Q1.long.biv_cell_table)
Q1.long.biv_cell_table <- add_strain(Q1.long.biv_cell_table)
Q1.long.biv_cell_table <- add_sex(Q1.long.biv_cell_table)
Q1.long.biv_cell_table <- add_subsp(Q1.long.biv_cell_table)

Q1_cell_long.biv <- ggplot(Q1.long.biv_cell_table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(sex~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,200))+geom_boxplot(alpha=.2) + ggtitle("Cell averages for Long Bivs")+theme(legend.position="none")
Q1_cell_long.biv

#mouse av for long biv
cell.av.long.biv.table <- ddply(male.long.biv, c("fileName"), summarise,

                        n_obs = length(Obj.ID),
                         mean.sc = mean(chromosomeLength)
                         )

cell.av.long.biv.table <- add_mouse(cell.av.long.biv.table)
cell.av.long.biv.table <- add_strain(cell.av.long.biv.table)
cell.av.long.biv.table <- add_subsp(cell.av.long.biv.table)

cell.avlong.biv <- ggplot(cell.av.long.biv.table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Cell av. \nMale Long Biv SC Lengths")
cell.avlong.biv

#mouse av for long biv
mouse.av.long.biv.table <- ddply(male.long.biv, c("mouse"), summarise,

                        n_obs = length(Obj.ID),
                         mean.sc = mean(chromosomeLength)
                         )

mouse.shoo.long.biv <- ggplot(mouse.av.long.biv.table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Mouse av. \nMale Long Biv SC Lengths")
mouse.shoo.long.biv

@@

Focus on comparing the differences between long.biv (and short biv once I make that dataset)

@@

```{r Q2.SC.long.biv, echo=FALSE}
male.long.biv <- real.long.bivData %>% filter(sex== "male")

shoo.long.biv <- ggplot(male.long.biv, aes(y=chromosomeLength, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Single Biv \nMale Long Biv SC Lengths")
shoo.long.biv

#mouse av for long biv
cell.av.long.biv.table <- ddply(male.long.biv, c("fileName"), summarise,

                        n_obs = length(Obj.ID),
                         mean.sc = mean(chromosomeLength)
                         )

cell.av.long.biv.table <- add_mouse(cell.av.long.biv.table)
cell.av.long.biv.table <- add_strain(cell.av.long.biv.table)
cell.av.long.biv.table <- add_subsp(cell.av.long.biv.table)

cell.avlong.biv <- ggplot(cell.av.long.biv.table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Cell av. \nMale Long Biv SC Lengths")
cell.avlong.biv

#mouse av for long biv
mouse.av.long.biv.table <- ddply(male.long.biv, c("mouse"), summarise,

                        n_obs = length(Obj.ID),
                         mean.sc = mean(chromosomeLength)
                         )

mouse.shoo.long.biv <- ggplot(mouse.av.long.biv.table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Mouse av. \nMale Long Biv SC Lengths")
mouse.shoo.long.biv

Not the pattern I expected, there might be more noise than I thought in this dataset.
